---
title: "Эконометрика, Осень 2021"
subtitle: "Лекция 4.</br>ММЛР. Пример, обсуждение."
author: "Владимир Пырлик"
date: "Октябрь 2021"
output:
  xaringan::moon_reader:
    mathjax: "https://cdn.bootcss.com/mathjax/2.7.1/MathJax.js?config=TeX-MML-AM_HTMLorMML"
    lib_dir: libs
    css: [libs/main.css, libs/fonts.css, libs/animate.css]
    chakra: libs/remark-latest.min.js
    nature:
      highlightStyle: github
      countIncrementalSlides: false
      highlightLines: true
      ratio: "8:5"

---
class: animated, fadeIn
```{r, echo=FALSE,eval=TRUE}
stargazer(dta2,type='text')
```

---
class: animated, fadeIn
```{r, echo=FALSE, fig.height = 9, fig.width = 16}
par(mfrow=c(1,2))
plot(x=within5km, y=log(dta1$price),pch='.',
     xlab="number of obj within 5 km",
     ylab="price, USD, log scale")
abline(lm1$coefficients, lwd=2, col='red')
legend('top',legend=c('data','regression line'),lwd=c(0,2),pch=c('.',''),col=c('black','red'),lty=c(0,1))
plot(x=within1km, y=log(dta1$price),pch='.',
     xlab="number of obj within 1 km",
     ylab="price, USD, log scale")
abline(lm(log(price)~1+within1km,data=dta2)$coefficients, lwd=2, col='red')
legend('top',legend=c('data','regression line'),lwd=c(0,2),pch=c('.',''),col=c('black','red'),lty=c(0,1))
```
 
---
class: animated, fadeIn
```{r, echo=FALSE}
stargazer(cf1,cf2,type='text')
```

---
class: animated, fadeIn
```{r, echo=FALSE}
stargazer(cf1,cf2,cf3,type='text')
```

---
class: animated, fadeIn
```{r, echo=FALSE}
stargazer(cf3,cf4,type='text')
```

---
class: animated, fadeIn
```{r, echo=FALSE}

```

---
class: animated, fadeIn
```{r, echo=FALSE}

```

---
class: animated, fadeIn
```{r, echo=FALSE}

```


---
class: animated, fadeIn
## 

---
class: animated, fadeIn
## 

---
class: animated, fadeIn
## 

---
class: animated, fadeIn
## 

---
class: animated, fadeIn
## 

---
class: animated, fadeIn
## 

---
class: animated, fadeIn
## 

---
class: animated, fadeIn
## 

